Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
fix typo

In order to obtain a sound synthesis of digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered. Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation may be written for the system in figure~\ref{fig:sampledsystem} considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller  ($\hat{C}(z)$):
\begin{equation}
\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
\end{equation}
that can be rewritten as follows:
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
\end{equation}
where
\begin{equation}
H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}
and
\begin{equation}
H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}

A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle. Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for BIBO stability of closed-loop system in figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.

>>>>

In order to obtain a sound synthesis of the digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered. Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation is written for the system in Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller ($\hat{C}(z)$):
\begin{equation}
\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
\end{equation}
that can be rewritten as follows:
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
\end{equation}
where
\begin{equation}
H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}
and
\begin{equation}
H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}

A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle. \textcolor{red}{Analyzing Eq.~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for BIBO stability of closed-loop system in Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.}
